The Proofs

### 2024-07-09 proofs/content.tex
edit and prepare for jfp

\PassOptionsToPackage{prologue,dvipsnames}{xcolor}

% \UseRawInputEncoding
% vim: ft=tex

% \documentclass[acmsmall,natbib=false]{article}
% \usepackage[a4paper, total={8in, 10in}]{geometry}

\documentclass[acmsmall,natbib=false,review,anonymous]{acmart}
\input{../prelude.tex}

\newcommand{\ottDir}{../ott/_gen}
\newcommand{\genDir}{_gen}
\input{\ottDir/defs.tex}
\input{\ottDir/renew-ott.tex}

\usepackage{../bibliography}
% \usepackage{amssymb}

% \usepackage[matha]{mathabx}

% https://tex.stackexchange.com/questions/85033/colored-symbols/85035#85035
% \newcommand*{\mathcolor}{}
% \def\mathcolor#1#{ \mathcoloraux{#1} }
% \newcommand*{\mathcoloraux}[3]{%
%   \protect\leavevmode
%   \begingroup
%   \color#1{#2}#3%
%   \endgroup
% }

\begin{document}

\title{The Proofs}

\maketitle

\tableofcontents

@@

\begin{figure}[ht]
  \begin{minipage}[t]{0.65\linewidth}
    \centering
      \begin{minipage}[t]{0.32\linewidth}
      \ottfundefnunpolP{}
      \end{minipage}
      \begin{minipage}[t]{0.32\linewidth}
      \ottfundefnunpolN{}
      \end{minipage}
    \caption{Type Depolarization}
    \label{fig:depolarization}
  \end{minipage}
  \hspace{0.5cm}
  \begin{minipage}[t]{0.3\linewidth}
    \centering
    \ottfundefnpolarP{}
    \caption{Type Polarization}
    \label{fig:polarization}
  \end{minipage}
\end{figure}

@@

\begin{figure}[h]
  \ottdefnELLabeled
  \caption{Subtyping elaboration from \fexists to \systemf}
  \label{fig:subt-elaboration}
\end{figure}

@@

\begin{figure}[h]
  \ottdefnELfPolLabeled{}
  \caption{Typing elaboration form from \systemf to \fexists}
  \label{fig:systemf-polarization}
\end{figure}

@@

\section{Theorem Statements: Declarative}
\subsection{Type Well-Formedness}
\input{\genDir/tex/wf-statements.tex}

\subsection{Substitution}
\input{\genDir/tex/subst-statements.tex}

\subsection{Declarative Subtyping}
\input{\genDir/tex/decl-subtyping-statements.tex}

\subsection{Equivalence}
\label{sec:decl-equiv-statements}
\input{\genDir/tex/equiv-statements.tex}

\subsection{Variable Ordering}
\input{\genDir/tex/ord-statements.tex}

\subsection{Normaliztaion}
\input{\genDir/tex/norm-statements.tex}

\section{Declarative Typing}
\input{\genDir/tex/decl-typing-statements.tex}

\section{Relation to \systemf}
\input{\genDir/tex/translation-statements.tex}

@@

\subsection{Algorithmic Type Well-formedness}
\input{\genDir/tex/wf-algo-statements.tex}

\subsection{Algorithmic Substitution}
\input{\genDir/tex/subst-algo-statements.tex}

\subsection{Algorithmic Normalization}
\input{\genDir/tex/norm-alg-statements.tex}

\subsection{Algorithmic Equivalence}
\input{\genDir/tex/equiv-alg-statements.tex}

\subsection{Unification Constraint Merge}
\input{\genDir/tex/unif-constraint-merge-statements.tex}

\subsection{Unification}
\input{\genDir/tex/unification-statements.tex}

\subsection{Anti-unification}
\input{\genDir/tex/au-statements.tex}

\subsection{Upper Bounds}
\label{sec:alg-upper-bounds-statements}
\input{\genDir/tex/lub-statements.tex}

\subsection{Upgrade}
\label{sec:upgrade-statements}
\input{\genDir/tex/upgrade-statements.tex}

\subsection{Constraint Satisfaction}
\input{\genDir/tex/constraint-sat-statements.tex}

\subsection{Positive Subtyping}
\input{\genDir/tex/alg-pos-subtyping-statements.tex}

\subsection{Subtyping Constraint Merge}
\input{\genDir/tex/constraint-merge-statements.tex}

\subsection{Negative Subtyping}
\input{\genDir/tex/alg-neg-subtyping-statements.tex}

\subsection{Singularity and Minimal Instantiation}
\input{\genDir/tex/singularity-statements.tex}

\subsection{Correctness of the Typing Algorithm}
\input{\genDir/tex/alg-typing-statements.tex}

@@

\subsection{Type Well-Formedness}
\input{\genDir/tex/wf-lemmas.tex}

\subsection{Substitution}
\input{\genDir/tex/subst-lemmas.tex}

\subsection{Declarative Subtyping}
\input{\genDir/tex/decl-subtyping-lemmas.tex}

\subsection{Equivalence}
\label{sec:decl-equiv-lemmas}
\input{\genDir/tex/equiv-lemmas.tex}

\subsection{Variable Ordering}
\input{\genDir/tex/ord-lemmas.tex}

\subsection{Normaliztaion}
\input{\genDir/tex/norm-lemmas.tex}

\section{Relation to \systemf}
\input{\genDir/tex/translation-proofs.tex}

@@

\subsection{Algorithmic Type Well-formedness}
\input{\genDir/tex/wf-algo-lemmas.tex}

\subsection{Substitution}
\input{\genDir/tex/subst-algo-lemmas.tex}

\subsection{Normalization}
\input{\genDir/tex/norm-alg-lemmas.tex}

\subsection{Equivalence}
\input{\genDir/tex/equiv-alg-lemmas.tex}

\subsection{Unification Constraint Merge}
\input{\genDir/tex/unif-constraint-merge-lemmas.tex}

\subsection{Unification}
\input{\genDir/tex/unification-lemmas.tex}\

\subsection{Anti-unification}
\input{\genDir/tex/au-lemmas.tex}

\subsection{Upper Bounds}
\label{sec:alg-upper-bounds-proofs}
\input{\genDir/tex/lub-lemmas.tex}

\subsection{Upgrade}
\label{sec:upgrade-lemmas}
\input{\genDir/tex/upgrade-lemmas.tex}

\subsection{Constraint Satisfaction}
\input{\genDir/tex/constraint-sat-lemmas.tex}

\subsection{Positive Subtyping}
\input{\genDir/tex/alg-pos-subtyping-lemmas.tex}

\subsection{Subtyping Constraint Merge}
\input{\genDir/tex/constraint-merge-lemmas.tex}

\subsection{Negative Subtyping}
\input{\genDir/tex/alg-neg-subtyping-lemmas.tex}

\section{Properties of the Declarative Typing}
\input{\genDir/tex/decl-typing-lemmas.tex}

@@

\subsection{Singularity and Minimal Instantiation}
\input{\genDir/tex/singularity-lemmas.tex}

\subsection{Correctness of the Typing Algorithm}
\input{\genDir/tex/alg-typing-lemmas.tex}

\printbibliography

\end{document}

>>>>

\newcommand{\proofGenDir}{_gen}

@@

\begin{figure}[t]
  \begin{minipage}[t]{0.65\linewidth}
    \centering
      \begin{minipage}[t]{0.32\linewidth}
      \ottfundefnunpolP{}
      \end{minipage}
      \begin{minipage}[t]{0.32\linewidth}
      \ottfundefnunpolN{}
      \end{minipage}
    \caption{Type Depolarization}
    \label{fig:depolarization}
  \end{minipage}
  \hspace{0.5cm}
  \begin{minipage}[t]{0.3\linewidth}
    \centering
    \ottfundefnpolarP{}
    \caption{Type Polarization}
    \label{fig:polarization}
  \end{minipage}
\end{figure}

@@

\begin{figure}[t]
  \ottdefnELLabeled
  \caption{Subtyping elaboration from \fexists to \systemf}
  \label{fig:subt-elaboration}
\end{figure}

@@

\begin{figure}[t]
  \ottdefnELfPolLabeled{}
  \caption{Typing elaboration form from \systemf to \fexists}
  \label{fig:systemf-polarization}
\end{figure}

@@

\section{Theorem Statements: Declarative}
\subsection{Type Well-Formedness}
\input{\proofGenDir/tex/wf-statements.tex}

\subsection{Substitution}
\input{\proofGenDir/tex/subst-statements.tex}

\subsection{Declarative Subtyping}
\input{\proofGenDir/tex/decl-subtyping-statements.tex}

\subsection{Equivalence}
\label{sec:decl-equiv-statements}
\input{\proofGenDir/tex/equiv-statements.tex}

\subsection{Variable Ordering}
\input{\proofGenDir/tex/ord-statements.tex}

\subsection{Normaliztaion}
\input{\proofGenDir/tex/norm-statements.tex}

\section{Declarative Typing}
\input{\proofGenDir/tex/decl-typing-statements.tex}

\section{Relation to \systemf}
\input{\proofGenDir/tex/translation-statements.tex}

@@

\subsection{Algorithmic Type Well-formedness}
\input{\proofGenDir/tex/wf-algo-statements.tex}

\subsection{Algorithmic Substitution}
\input{\proofGenDir/tex/subst-algo-statements.tex}

\subsection{Algorithmic Normalization}
\input{\proofGenDir/tex/norm-alg-statements.tex}

\subsection{Algorithmic Equivalence}
\input{\proofGenDir/tex/equiv-alg-statements.tex}

\subsection{Unification Constraint Merge}
\input{\proofGenDir/tex/unif-constraint-merge-statements.tex}

\subsection{Unification}
\input{\proofGenDir/tex/unification-statements.tex}

\subsection{Anti-unification}
\input{\proofGenDir/tex/au-statements.tex}

\subsection{Upper Bounds}
\label{sec:alg-upper-bounds-statements}
\input{\proofGenDir/tex/lub-statements.tex}

\subsection{Upgrade}
\label{sec:upgrade-statements}
\input{\proofGenDir/tex/upgrade-statements.tex}

\subsection{Constraint Satisfaction}
\input{\proofGenDir/tex/constraint-sat-statements.tex}

\subsection{Positive Subtyping}
\input{\proofGenDir/tex/alg-pos-subtyping-statements.tex}

\subsection{Subtyping Constraint Merge}
\input{\proofGenDir/tex/constraint-merge-statements.tex}

\subsection{Negative Subtyping}
\input{\proofGenDir/tex/alg-neg-subtyping-statements.tex}

\subsection{Singularity and Minimal Instantiation}
\input{\proofGenDir/tex/singularity-statements.tex}

\subsection{Correctness of the Typing Algorithm}
\input{\proofGenDir/tex/alg-typing-statements.tex}

@@

\subsection{Type Well-Formedness}
\input{\proofGenDir/tex/wf-lemmas.tex}

\subsection{Substitution}
\input{\proofGenDir/tex/subst-lemmas.tex}

\subsection{Declarative Subtyping}
\input{\proofGenDir/tex/decl-subtyping-lemmas.tex}

\subsection{Equivalence}
\label{sec:decl-equiv-lemmas}
\input{\proofGenDir/tex/equiv-lemmas.tex}

\subsection{Variable Ordering}
\input{\proofGenDir/tex/ord-lemmas.tex}

\subsection{Normaliztaion}
\input{\proofGenDir/tex/norm-lemmas.tex}

\section{Relation to \systemf}
\input{\proofGenDir/tex/translation-proofs.tex}

@@

\subsection{Algorithmic Type Well-formedness}
\input{\proofGenDir/tex/wf-algo-lemmas.tex}

\subsection{Substitution}
\input{\proofGenDir/tex/subst-algo-lemmas.tex}

\subsection{Normalization}
\input{\proofGenDir/tex/norm-alg-lemmas.tex}

\subsection{Equivalence}
\input{\proofGenDir/tex/equiv-alg-lemmas.tex}

\subsection{Unification Constraint Merge}
\input{\proofGenDir/tex/unif-constraint-merge-lemmas.tex}

\subsection{Unification}
\input{\proofGenDir/tex/unification-lemmas.tex}\

\subsection{Anti-unification}
\input{\proofGenDir/tex/au-lemmas.tex}

\subsection{Upper Bounds}
\label{sec:alg-upper-bounds-proofs}
\input{\proofGenDir/tex/lub-lemmas.tex}

\subsection{Upgrade}
\label{sec:upgrade-lemmas}
\input{\proofGenDir/tex/upgrade-lemmas.tex}

\subsection{Constraint Satisfaction}
\input{\proofGenDir/tex/constraint-sat-lemmas.tex}

\subsection{Positive Subtyping}
\input{\proofGenDir/tex/alg-pos-subtyping-lemmas.tex}

\subsection{Subtyping Constraint Merge}
\input{\proofGenDir/tex/constraint-merge-lemmas.tex}

\subsection{Negative Subtyping}
\input{\proofGenDir/tex/alg-neg-subtyping-lemmas.tex}

\section{Properties of the Declarative Typing}
\input{\proofGenDir/tex/decl-typing-lemmas.tex}

@@

\subsection{Singularity and Minimal Instantiation}
\input{\proofGenDir/tex/singularity-lemmas.tex}

\subsection{Correctness of the Typing Algorithm}
\input{\proofGenDir/tex/alg-typing-lemmas.tex}
